Untitled

### 2017-02-15 Code/calculate_std_mort_rates.Rmd

    mortality.rates.summary <- mortality.rates %>% group_by(state.n, year.n, race.n, sex.n, COD) %>%
      summarise(race = first(race),
                sex = first(sex),
                state = first(state),
                year = first(year),
                age.std.mortality.rate_LCL = quantile(age.std.mortality.rate, 0.025), #summarize across posterior samples (post.samp)
                age.std.mortality.rate_med = quantile(age.std.mortality.rate, 0.5),
                age.std.mortality.rate_UCL = quantile(age.std.mortality.rate, 0.0975))

@@

    mortality.rates.difference <- mortality.rates.wide %>% 
      group_by(state.n, year.n, sex.n, COD) %>%
      summarise(rate.difference_LCL = quantile(rate.difference, 0.025), #summarize across posterior samples (post.samp)
                rate.difference_med = quantile(rate.difference, 0.5),
                rate.difference_UCL = quantile(rate.difference, 0.0975),
                sex = first(sex),
                state = first(state),
                year = first(year))

>>>>

    mortality.rates.summary <- mortality.rates %>% group_by(state.n, year.n, race.n, sex.n, COD) %>%
      summarise(race = first(race),
                sex = first(sex),
                state = first(state),
                year = first(year),
                age.std.mortality.rate_LCL = quantile(age.std.mortality.rate, 0.025), #summarise across posterior samples (post.samp)
                age.std.mortality.rate_med = quantile(age.std.mortality.rate, 0.5),
                age.std.mortality.rate_UCL = quantile(age.std.mortality.rate, 0.975))

@@

    mortality.rates.difference <- mortality.rates.wide %>% 
      group_by(state.n, year.n, sex.n, COD) %>%
      summarise(rate.difference_LCL = quantile(rate.difference, 0.025), #summarize across posterior samples (post.samp)
                rate.difference_med = quantile(rate.difference, 0.5),
                rate.difference_UCL = quantile(rate.difference, 0.975),
                sex = first(sex),
                state = first(state),
                year = first(year))
